Positivity-Preserving Adaptive Runge-Kutta Methods

### 2020-03-09 latex/Image_b_convex.tex
Multiple small corrections
overview.tex:
spelling mistakes and minor notation changes
Changed the second example to make it more reasonable
TODOs: Abstract, Introduction, Formulation LPs, Numerical results, Conclussion

Bib_RK_optim.bib:
Hairer as complete book 

Image_b_direct.tex:
Notation change

Image_b_convex.tex:
Notation change, 
Make it fit into context of direct adaptation

\begin{tikzpicture}
    % Draw axes
	\coordinate (borig) at (1,2.3);
    \coordinate (b_a) at (0.8,0.8);
	\coordinate (b_b) at (2.3,1);
	\coordinate (b) at (1.1,1.5);

@@

    \draw[thick,red,fill = red!20] (borig) -- (b_a) -- (b_b) -- cycle;

	\draw[thick,->] (0,0) -- node[anchor=south west,pos = 0.95] {$b_{orig}$} (borig);
    \draw[thick,->] (0,0) -- node[anchor=south west,pos = 0.95] {$b_b$} (b_a);
    \draw[thick,->] (0,0) -- node[anchor=south west,pos = 0.95] {$b$} (b);
	\draw[thick,->] (0,0) -- node[anchor=north west,pos = 0.8,fill=white] {$b_b$} (b_b);

>>>>

\begin{tikzpicture}
    % Draw axes

	\coordinate (bo) at (1.2,1.8);
    \coordinate (b) at (2,1);
    \coordinate (db) at ($(b)-(bo)$);
    \coordinate (b1) at ($0.4*(db)+(b)$);
    \coordinate (b0) at ($-0.2*(db)+(bo)$);;

@@

%\draw[thick,red,*-*] (b0) -- (b1);
   \node[circle,inner sep=1.5pt,draw,fill,red] (A) at (b0) {};
   \node[circle,inner sep=1.5pt,draw,fill,red] (B) at (b1) {};
   \draw[thick,red,-] (b0) -- (b1);

	\draw[thick,->] (0,0) -- node[anchor=south east,pos = 0.8] {$b_{a}$} (b0);
    \draw[thick,->] (0,0) -- node[anchor=south east,pos = 0.8] {$\tilde{b}$} (b);
    \draw[thick,->] (0,0) -- node[anchor=north west,pos = 0.8] {$b_{b}$} (b1);
